\subsection{
Write a program that prints your favorite movie name. It should print director name on the next line.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/01.sh}
\subsection{
Write a shell script that prints out your name and waits for the user to press the [Enter] key before the script ends.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/02.sh}
\subsection{
List 10 builtin and external commands.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/03.sh}

\subsection{
Make a backup of existing variable called PS1 to OLDPS1. Set PS1 to \$. Reset your prompt using OLDPS1 variable.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/05.sh}
\subsection{
Customize your bash prompt by setting PS1 variable to "I Love Scripting".
}
\inputminted[breaklines, linenos]{shell}{25-09-2020/06.sh}
\subsection{
Edit your .bashrc file and set your new PS1 variable.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/07.sh}
\subsection{
Write a command to display the environment.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/08.sh}

\subsection{
Write a shell script that allows a user to enter his or her top three ice cream flavors. Your script should then print out the name of all three flavors.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/09.sh}

\subsection{
Write a shell script that allows a user to enter any Internet domain name (host name such as www.cyberciti.biz). Your script should than print out the IP address of the Internet domain name.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/10.sh}
\subsection{
Write a shell script that allows a user to enter any existing file name. The program should then copy file to /tmp directory.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/11.sh}
\subsection{
Write a shell script that allows a user to enter directory name. The program should then create directory name in /tmp directory.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/12.sh}
\subsection{
Write a shell script that allows a user to enter three file names. The program should then copy all files to USB pen.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/13.sh}
\subsection{
Write a simple shell script where the user enters a pizza parlor bill total. Your script should then display a 10 percent tip.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/14.sh}

\subsection{
Write a simple calculator program that allows user to enter two numeric values and operand as follows. The program should then print out the sum of two numbers. Make sure it works according to entered operand.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/16.sh}
\subsection{
Write a shell script that display one of ten unique fortune cookie message, at random each it is run.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/17.sh}
\subsection{
Write a shell script that, given a file name as the argument will count vowels, blank spaces, characters, number of line and symbols.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/18.sh}
\subsection{
Write a shell script that, given a file name as the argument will count English language articles such As 'A', 'An' and 'The'.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/19.sh}
\subsection{
Write a shell script that, given a file name as the argument will write the even numbered line to a file with name evenfile and odd numbered lines in a text file called oddfile.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/20.sh}
\subsection{
Write a shell script to monitor Linux server disk space using a while loop. Send an email alert when percentage of used disk space is greater than or equal to 90\%.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/21.sh}
\subsection{
Write a shell script to determine if an input number is a palindrome or not.}

\inputminted[breaklines, linenos]{shell}{25-09-2020/22.sh}
\subsection{
Write a shell program to read a number and find the sum of digits.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/23.sh}
\subsection{
Write a shell program to read a number and display reverse the number.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/24.sh}
\subsection{
Write a shell script that will count the number of files in each of your sub-directories using the for loop.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/25.sh}
\subsection{
Write a shell script that will count the number of files in each of your sub-directories using the for loop.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/26.sh}
\subsection{
Write a shell script that accepts two directory names as arguments and deletes those files in the first directory which are similarly named in the second directory.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/27.sh}
\subsection{
Write a shell script to search for no password entries in /etc/passwd and lock all accounts.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/28.sh}
\subsection{
Write a shell program to read two numbers and display all the odd numbers between those two numbers.
}

\inputminted[breaklines, linenos]{shell}{25-09-2020/29.sh}
